Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-24 latex/ms.tex
write theory section something, #6
remove Wiley-formed tex

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{moreverb}
\usepackage{lineno}
\linenumbers
\usepackage[doublespacing]{setspace}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\articletype{Research article, \today}%

\received{<day> <Month>, <year>}
\revised{<day> <Month>, <year>}
\accepted{<day> <Month>, <year>}

%\raggedbottom

\begin{document}

\title{Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}}

\author[1]{Tetsuya Akita}
\authormark{Akita}

\address[1]{\orgdiv{Fisheries Data Sciences Division}, \orgname{Fisheries Resources Institute}, \orgaddress{\state{Kanagawa}, \country{Japan}}}

\corres{*Tetsuya Akita, Fisheries Data Sciences Division, Fisheries Resources Institute, FRA, 236-8648 Kanagawa, Japan. \email{akitatetsuya1981@affrc.go.jp}}

%\presentaddress{Present address}

\abstract[Abstract]{The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements:

Point 1: set the context for and purpose of the work;

Point 2: indicate the approach and methods;

Point 3: outline the main results;

Point 4: identify the conclusions and the wider implications.

1. aaa\\
2. bbb

本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。}

\keywords{Close-kin mark recapture; Half-sibling; Population structure}

\maketitle

%\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

\section{Introduction}\label{sec1}

@@

\renewcommand{\arraystretch}{0.6}
\begin{table}[tb]
\begin{center}
   \caption[]{The list of mathematical symbols employed in the main text}
    \textbf {}\\[-4mm]
    \begin{tabular}{llc} \hline
       & & \\
	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
		                						& \\
	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
		                						& \\
	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
		                						& \\
	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
		                						& \\
	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
	                							& shares a parent-offspring relationship within the population 1 and 2\\
									& \\
	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
	                							& shares a parent-offspring relationship between the population 1 and 2\\
									& \\
	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
	                							& shares a half-sibling relationship between the population 1 and 2\\
					                			& \\
	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
		                						& \\
	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
		                						& \\
	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
	                							& \\
	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
	                							& \\              		
	\hline
    \end{tabular}
    \label{symbols} 
\end{center} 
\end{table}
\renewcommand{\arraystretch}{1}

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 once a year. In this study, a mature individual is called a parent even if it does not produce offspring.

Suppose there are $N_1$ parents in the population 1 at the beginning of year and there are $N_2$ parents in the population 2 at the beginning of the next year. There are $M$ survived parents at the beginning of the next year that are moved from population 1 to population 2. 各親は繁殖ポテンシャルに従って、子供を残すとしよう。For the explanation purpose, lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。

どのように子供を産むのか。我々のモデルは、フレキシブルな仮定に対応できるが詳細は付録に

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{Example of relationships between mothers and their offspring number. The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively. The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$). The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively. The symbol x denotes a failure to survive at sampling. Sampled individuals are denoted with squares. Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$. The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.	}
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%

@@

@@

\begin{comment}%%%%%%%%%%%%%%%
まず最初に，最もシンプルなモデルを考える。$t$年にサブ集団１にいる$N_{1,t}$個体の母親を考えよう。$t$年に子供を産んだ後，$N_{1,t}$個体のうち$M_{1\to2}$個体がサブ集団２に移動し，$t+1$年にサブ集団２にいる母個体$N_{2,t+1}$の一部として子供を産むとする。この時，サブ集団１から$t$年に産まれた子供とサブ集団２から$t+1$年に産まれた子供が，母を共有する兄弟(Maternal half Sibling, MHS)である確率$\pi_{\rm b,1\to2}$を考える。どの母親も同じような繁殖ポテンシャルを持つと仮定すると，移動する母親の子供をサブ集団１でサンプルする確率は$M_{1\to2}/N_{1,t}$となる。同様に，移動する母親の子供をサブ集団２においてサンプルする確率は$M_{1\to2}/N_{2,t+1}$である。それぞれでサンプルした子供の母親が同一である確率は$1/M_{1\to2}$であることより，サンプルした２個体がMHSペアとなる確率が以下のように得られる。
\begin{align}
\pi_{\rm b,1\to2} &= \frac{M_{1\to2}}{N_{1,t}} \frac{M_{1\to2}}{N_{2,t+1}} \frac{1}{M_{1\to2}} \nonumber\\
&= \frac{M_{1\to2}}{N_{1,t}N_{2,t+1}}
\label{1-1}
\end{align}
サブ集団１からサブ集団２に移動する割合$m_{1\to2}$を導入することで，上式は
\begin{align}
\pi_{\rm b,1\to2} &= \frac{m_{1\to2}}{N_{2,t+1}}
\label{1-2}
\end{align}
と書ける。$M_{1\to2} = m_{1\to2}N_{1,t}$とした。$m_{1\to2}$には移動だけでなく$t+1$年の産卵までの生存確率が含まれている点に注意。

MHSペアとなる確率が得られれば，サンプル数に応じて見つかるMHSペア$H_{1\to2}$の期待値が得られる。
\begin{align}
\mathbb{E}[H_{1\to2}] &= \pi_{\rm b,1\to2} n_{1,t} n_{2,t+1} \nonumber\\
&= \frac{m_{1\to2}n_{1,t} n_{2,t+1}} {N_{2,t+1}}
\label{1-3}
\end{align}
$n_{1,t}, n_{2,t+1}$は，それぞれサブ集団１（$t$年）でのサンプル数，サブ集団２（$t+1$年）でのサンプル数である。この結果から，平均的にみて少なくとも１ペア以上を見出すには，(親魚尾数)の平方根のオーダー以上のサンプル数が要求されることがわかる。以上より，見出されたMHSペア数から母親の移動率に関する線形推定量が得られる。
\begin{align}
\widehat{m_{1\to2}} &= \frac{N_{2,t+1} H_{1\to2,{\rm obs}} } {n_{1,t}n_{2,t+1}}
\label{1-4}
\end{align}
ハットは推定量を表し，obsの添字は観測値であることを表す。

\subsection{Two-way movement}

次に，反対方向の移動について考える。すなわち，$t$年にサブ集団２にいる$N_{2,t}$個体の母親から，$M_{1\to2}$個体が$t+1$年にサブ集団１へ移動すること考えよう。これまで同様に考えて，MHSペアとなる確率は，
\begin{align}
\pi_{\rm b,2\to1} &= \frac{m_{2\to1}}{N_{1,t+1}}
\label{2-1}
\end{align}
のようになり，移動率に関する推定量
\begin{align}
\widehat{m_{2\to1}} &= \frac{N_{1,t+1} H_{2\to1,{\rm obs}} } {n_{2,t}n_{1,t+1}}
\label{2-2}
\end{align}
が得られる。すなわち，移動が一方向であろうが双方向であろうが，各方向の移動率に関する推定量は式\ref{1-4}と式\ref{2-2}から独立に得られる。したがって，以降の導出ではサブ集団１からサブ集団２に移動する個体についてだけ考え，添字を省略する。例えば，$N_1$という記載は，$t$年に親魚として存在した個体数を表す。

\subsection{Two-sex}

ここまでは、母親を介した兄弟ペアと、母親の個体数およびその移動について考えてきた。しかしながら、母親を介した兄弟か父親を介した兄弟かを見分けるには、ミトコンドリアの情報を用いた類推が必須である点、当歳魚のサンプル数が同程度でも区別しない半兄弟ペアの半数程度しか発見されない点などから、実際の応用では区別しない半兄弟ペアを用いるほうが望ましい。そこで、まずは性比=1:1（すなわち，$N_{\rm male}=N_{\rm female}=N_1/2$かつ$M_{\rm male}=M_{\rm female}=M/2$）でランダム交配を仮定した集団を考えよう。この時、サブ集団１でサンプルした当歳魚の親が移動する親個体である確率は$M_{\rm male}/N_{\rm male} + M_{\rm female}/N_{\rm female}=2M/N_1$となる。同様に，移動した親の子供をサブ集団２においてサンプルする確率は$2M/N_2$であることから，
\begin{align}
\pi &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{4M}{N_{1}N_{2}}
\label{3-1}
\end{align}
が得られる。その結果，移動率の推定値は新たに係数4が分母に加わって
\begin{align}
\widehat{m} &= \frac{N_{2} H_{\rm obs} } {4n_{1}n_{2}}
\end{align}
となる。

ここでは応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数($N$)・移動率($m$)・生存率($s$)を推定する理論的な枠組みを提示する。サブ集団１に生息する親魚数を、$N_1(t), N_1(t+1), N_1(t+2)$のように表記し、他のパラメータについても同様とする。個体数については６つのパラメータ、移動率および生存率は４つのパラメータとなり、合計１４のパラメータが考えられる（$t+2$年の移動率および生存率は含まれない点に注意）。まずは、これら１４個のパラメータは独立に決まるとしよう（すなわち、$N_1(t)$と$N_1(t+1)$は無関係で、$s_1(t)$と$s_1(t+1)$は独立に決める、など）。なお、この応用例では、移動する親魚は繁殖ポテンシャルによらずに決まると仮定して、式\ref{4-1}を用いることにしよう。また、全ての親魚は、年をまたぐごとに、1)サブ集団を移動して産卵するか（確率：$m$）、2)同じサブ集団に留まって産卵するか（確率：$s$）、3)死亡するか（確率：$1-m-s$）、のいずれかのイベントを経験するとする。

今回新たに開発した移動に関する関係式について、以下の６種類の親魚に関するその子供（当歳魚）ペアがありえる：
\begin{enumerate}
  \item $N_1(t)\to N_2(t+1)$
  \item $N_1(t)\to N_2(t+2)$
  \item $N_1(t+1)\to N_2(t+2)$
  \item $N_2(t)\to N_1(t+1)$
  \item $N_2(t)\to N_1(t+2)$
  \item $N_2(t+1)\to N_1(t+2)$
\end{enumerate}
右向きの矢印$\to$は、興味ある親魚が年を跨いだ後どのサブ集団に属しているかを表している。１番目を例にとると、$t$年にサブ集団１から、$t+1$年にサブ集団２からそれぞれ当歳魚をサンプルすることを意味する。加えて、同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式についても、以下の６種類が考えられる：
\begin{enumerate}
\setcounter{enumi}{6}
  \item $N_1(t)\to N_1(t+1)$
  \item $N_1(t)\to N_1(t+2)$
  \item $N_1(t+1)\to N_1(t+2)$
  \item $N_2(t)\to N_2(t+1)$
  \item $N_2(t)\to N_2(t+2)$
  \item $N_2(t+1)\to N_2(t+2)$
\end{enumerate}
以上の、合計１２種類の式を連立できることを示した。最大１４個のパラメータが必要となるのであったが、パラメータ数を応用先に応じて適宜減少させることができる場合、興味あるパラメータを推定することができる。

ちなみに、同一年内に同じサブ集団内で見つかるMHSペアについては、有効集団サイズの情報（正確には有効繁殖サイズ、Effective breeding size）は持っているが、センサスサイズに関するダイレクトな情報は持っていない点に注意。
\end{comment}%%%%%%%%%%%%%%%

\section{Results and Discussion}\label{sec4}

オーダーは$m\approx0.1$程度を想定。これよりもずっと小さければ、遺伝的に異なる系群と考えられFstも大きく出るので、ベイズアスなどから推定できるだろう。一方、その場合はサンプル数が大量になり、今回提案した方法は向かない。

\section{ACKNOWLEDGEMENTS}

The author thanks MV Bravington for motivating me to pursue this research topic. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.

>>>>

\documentclass[12pt, English]{article}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
%\usepackage{apacite}
\usepackage[natbibapa]{apacite}
%\renewcommand{\APACrefYearMonthDay}[3]{\APACrefYear{#1} 
%  \cite<pre>[post]{key}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{boxedminipage}
\usepackage{oldgerm}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{indentfirst}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{lscape} 
\usepackage[mathlines]{lineno}
\renewcommand{\ttdefault}{mathptmx}
\usepackage[latin9]{inputenc}
\usepackage{bm}
\usepackage{relsize}
\usepackage[normalem]{ulem} %%
%\linenumbers
\usepackage{bm}
\setlength{\parindent}{20pt}
\usepackage[labelformat=empty,labelsep=none]{caption}
\usepackage[singlelinecheck=false]{caption}
\usepackage{color}
\def\RED#1{\textcolor{black}{#1}} %% 
\def\BLUE#1{\textcolor{blue}{#1}} %% 
\begin{document}

\title{Estimating migration rates for iteroparous species using kinship pairs found between populations}
\author{
Tetsuya Akita$^{a}$\thanks{
\emph{Corresponding author}:
    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
   \small Kanagawa, 236-8648, Japan.
   }
\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
\maketitle

\begin{abstract}
本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。
\\
\end{abstract}
\textbf{Key words:} effective population size; sibship assignment; overdispersed reproduction; close-kin mark-recapture\\
\textbf{Running head:} Estimating migration rates using kinship pairs\\

\pagebreak
\begin{spacing}{1.9}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%FIGURE S1%%%
\newcommand{\NeNbias}{S1}
%%%%%%%%%%%

%%%FIGURE S2%%%
\newcommand{\Nebias}{S2}
%%%%%%%%%%%

%%%FIGURE S3%%%
\newcommand{\Ninvbias}{S3}
%%%%%%%%%%%

%%%FIGURE S4%%%
\newcommand{\NeNcv}{S4}
%%%%%%%%%%%

%%%FIGURE S5%%%
\newcommand{\Necv}{S5}
%%%%%%%%%%%

%%%FIGURE S6%%%
\newcommand{\Ninvcv}{S6}
%%%%%%%%%%%

\section{INTRODUCTION}

@@

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate. In this framework, two reproductive seasons (hereafter, we call them "the first year" and "the second year") are enough to estimate it.

Suppose there are $N_1$ parents in the population 1 at the beginning of the first year. Each parent produces offspring in which the number is determined by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$). After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$). Similar to the population, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).

どのように子供を産むのか。我々のモデルは、フレキシブルな仮定に対応できるが詳細は付録に
In this study, a mature individual is called a parent even if it does not produce offspring.

@@

@@

Here we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.

For the explanation purpose,

lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。

Assuming that every fathers in the population 1 has a same reproductive potential, どの母親も同じような繁殖ポテンシャルを持つと仮定 すると，移動する母親の子供をサブ集団1でサンプルする確率は$rM/rN$...となる。

@@

The estimation of the ratio of the contemporary effective population size to the census size ($N_{\rm e}/N$) has attracted much research attention for providing information about a current population, especially in the context of conservation biology and wildlife management \cite[]{Palstra_2012,FRANKHAM201456}. Small $N_{\rm e}/N$ demonstrates large variance in reproductive success \cite[]{Wang:2016aa, JFB:JFB13143, Akita_2019}, resulting from the variance of reproductive potential \cite[e.g., the big old fat fecund female fish hypothesis;][]{Hixon_2014} or from the situation in which only some families successfully reproduce \cite[referred to as the ``Sweepstakes reproductive success'' hypothesis,][]{hedgecock2011sweepstakes}. Moreover, if $N_{\rm e}/N$ is invariant across years, then $N_{\rm e}$ may behave like an index of $N$, and vice versa \cite[]{luikart2010estimation}. However, if $N_{\rm e}/N$ fluctuates across years, the trends can clarify the interpretation of environmental and/or anthropological factors, causing the variance of reproductive potential, family-correlated survivorship, or fluctuating population dynamics. Besides, low precision and/or large bias for estimating $N_{\rm e}/N$ may lead to a wrong interpretation of the population \cite[]{Tallmon:2012aa}.

The estimation of $N_{\rm e}/N$ has been performed by utilizing the estimated values of contemporary effective population size ($N_{\rm e}$) and census size ($N$), unless complete pedigree data and/or full census data are available. Additionally, there are numerous methods for estimating $N_{\rm e}$ from genetic markers \cite[][and the references contained therein]{Wang:2016aa}. There are also numerous methods for estimating $N$, such as a mark-recapture method or population dynamics modeling with survey data \cite[e.g.,][]{seber1982estimation,quinn1999quantitative,kery2011bayesian,methot2013stock}. It is known that there are large variations in both estimators; thus, their combination (i.e., the estimator of $N_{\rm e}/N$) also shows large variation \cite[]{Palstra_2012,Marandel_2018}. There is currently a little theoretical foundation for the estimator of $N_{\rm e}/N$, indicating no guidance for a sample size to ensure the required accuracy and precision.

Close-kin mark-recapture (CKMR) is a recently developed method for estimating $N$ that utilizes the information about kinship in a sample. This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}. Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in mark-recapture. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$. While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}. This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.

In this study, we propose a new method for estimating the ratio of contemporary effective mother size to the census size ($N_{\rm e,m}/N_{\rm m}$) in a population, as a proxy of $N_{\rm e}/N$. Assuming that kinships are genetically detected without any error, this method is based on the numbers of maternal-sibling (MS) and mother--offspring (MO) pairs in a sample. Sampling is completed at a single breeding time; sampling offspring within the same cohort and mothers probably shares MO relationship with sampled offspring. Our model provides a nearly unbiased estimator of $N_{\rm e,m}/N_{\rm m}$ that explicitly incorporates two types of overdispersed reproduction \cite[i.e., parental and nonparental variations;][]{Akita_2019}, making it possible to target a species that shows iteroparity (i.e., multiple reproductive cycles during the lifetime) and/or sweepstakes reproductive success. This estimator applying an iteroparous species corresponds to the estimator of the ratio of contemporary effective breeding mother size to the census size, $N_{\rm b,m}/N_{\rm m}$. First, we explain the modeling assumption and sampling scheme. Then, we analytically determine (nearly) the unbiased estimators of $N_{\rm e,m}$, $ 1/N_{\rm m}$, and $N_{\rm e,m}/N_{\rm m}$, which are based on the numbers of MS and/or MO pairs. Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size. It is noteworthy that our modeling framework can be applied to diverse animal species. However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{THEORY}\label{theory}

In this section, we present the theoretical foundation for estimating $N_{\rm e,m}/N_{\rm m}$. The estimator is based on previous studies that provides the estimator of $N_{\rm e,m}$ \cite[]{Akita_2019} and $1/N_{\rm m}$ \cite[]{Akita2018}. The main contribution of this paper is formulation of the estimator of $N_{\rm e,m}/N_{\rm m}$, presented in Eq.~\ref{NeN_hat2}. The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hypothetical population}

We suppose that there is a hypothetical population comprising $N_{\rm m}$ mothers and there is also no population subdivision or spatial structure. In this study, a mature female is called a mother even if she does not produce offspring. For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season. Following \cite{Akita_2019}, our modeling framework employs two types of overdispersed reproduction: parental and nonparental variations. Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating opportunities of the mother and the number of her offspring). {\bf Figure~1} illustrates a schematic diagram of the effects of parental and nonparental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population. Detailed definitions of parental and nonparental variations are stated in \cite{Akita_2019}. {\bf Appendix A} provides the theoretical foundation of both parental and nonparental variations in reproduction.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sampling}

To obtain the estimator of $N_{\rm e,m}/N_{\rm m}$, we utilize the number of MS and MO pairs observed in a sample. For the mathematical tractability, only one reproductive season is targeted for sampling. Thus, the sampling method does not affect our modeling framework whether it is invasive or noninvasive. In the population, $n_{\rm M}$ mothers are randomly sampled immediately after the end of the reproductive season. Additionally, in the population, $n_{\rm O}$ offspring are also randomly sampled. The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively). As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed. In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Linking $N_{\rm e,m}/N_{\rm m}$ to kinship relationships}

In this subsection, we provide the theoretical foundation for understanding how $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships in a population, based on work presented in previous studies. The rationale is that the observed number of MS and MO pairs have information about $N_{\rm e,m}$ and $N_{\rm m}$, respectively, as noted below.

First, we consider the relationship between the number of MS pairs and $N_{\rm e,m}$. \cite{Akita_2019} defined the contemporary effective mother size as follows: 
\begin{equation}
N_{\rm e,m} = \frac{1}{\pi_{\rm MS}},
\label{Ne}
\end{equation}
where $\pi_{\rm MS}$ denotes the probability that two offspring share an MS relationship with an arbitrary mother. This definition is related to the inbreeding effective population size \cite[]{nordborg2002separation,wang2009new}. When sampling from a single cohort in a population with overlapping generations, the effective mother size in our definition corresponds to the effective breeding mother size per breeding-time unit (e.g., year), which produces the single cohort and is denoted by $N_{\rm b,m}$ \cite[]{waples1991genetic}. Hereafter, the description of the model focuses on species with discrete generations; thus, we use $N_{\rm e,m}$ to denote the contemporary effective mother size, although $N_{\rm b,m}$ is the appropriate notation in the left-hand side of Eq.~\ref{Ne} when the target species is iteroparous with overlapping generations, as exemplified in {\bf Appendix B}.

Given the total mother number and the degree of overdisepered reproduction in the population, \cite{Akita_2019} derived $\pi_{\rm MS}$, which is approximately given by
\begin{equation}
\pi_{\rm MS} \approx \frac{c}{N_{\rm m}+c-1},
\label{pi_MS}
\end{equation}
where $c$ indicates combined effect of both parental and nonparental variations and satisfies $\ge1$. Without either parental or nonparental variation (i.e., $c\to1$, see details in {\bf Appendix C}), $\pi_{\rm MS}$ converges to $1/N_{\rm m}$, corresponding to the Poisson variance in reproduction for all mothers. The mathematical description of $c$ is briefly summarized in {\bf Appendix C}.

Next, we consider the relationship between the number of MO pairs and $N_{\rm m}$. It is natural to consider that the probability of a randomly sampled mother and her offspring sharing an MO relationship (denoted by $\pi_{\rm MO}$) can be associated with the total mother number, given by
\begin{equation}
\pi_{\rm MO} = \frac{1}{N_{\rm m}}.
\label{pi_MO}
\end{equation} 
It is noteworthy that $\pi_{\rm MO}$ is independent of the distribution of the offspring number \cite[]{Akita2018}.

Together with Eqs.~\ref{Ne} and \ref{pi_MO}, we finally obtain the ratio of the effective mother size to census size as follows: 
\begin{equation}
\frac{N_{\rm e,m}}{N_{\rm m}} = \frac{\pi_{\rm MO}}{\pi_{\rm MS}},
\label{NeN}
\end{equation}
indicating that $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships (i.e., MS and MO) in a population. In other words, when $1/\pi_{\rm MS}$ and $\pi_{\rm MO}$ is estimated from observed MS and MO pairs, respectively, the ratio can also be estimated. Meanwhile, \cite{Akita_2019} obtained an alternative formulation of the ratio using Eqs.~\ref{Ne} and \ref{pi_MS}: 
\begin{eqnarray}
\frac{N_{\rm e,m}}{N_{\rm m}} &=& \frac{1}{\pi_{\rm MS}} \frac{1}{N_{\rm m}} \nonumber\\
&\approx& \frac{1}{c},  
\label{NeN}
\end{eqnarray}
where $N_{\rm m} \gg 1$ is assumed for approximation. This theoretical connection indicates that estimating $N_{\rm e,m}/N_{\rm m}$ corresponds to estimating $1/c$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimator of $N_{\rm e,m}/N_{\rm m}$}

This subsection proposes the estimator of $N_{\rm e,m}/N_{\rm m}$  as follows:
\begin{equation}
\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } = \widehat{N_{\rm e,m}}\widehat{\left(\frac{1}{N_{\rm m}}\right)}.
\label{NeN_hat1}
\end{equation}
A ``hat'' denotes the estimator of a variable in this study. The requisite condition that satisfies Eq.~\ref{NeN_hat1} is independent of $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$. This property will be shown later in this subsection. \cite{Akita_2019} derived the nearly unbiased estimator of $N_{\rm e,m}$, which is given by 
\begin{eqnarray}
\widehat{N_{\rm e,m}} &=& \widehat{\left(\frac{1}{\pi_{\rm MS}}\right)}\nonumber\\
 &=& \frac{\binom{n_{\rm O}}{2}+1}{H_{\rm MS}^{\rm obs}+1},
\label{Ne_hat}
\end{eqnarray}
where $H_{\rm MS}^{\rm obs}$ denotes the observed number of MS pairs in a sample. This estimator works well unless $n_{\rm O}$ is very small, which is based on the idea that the observation of $1/(H_{\rm MS} + 1)$ approximately provides a linear estimator of $N_{\rm e,m}$.

Next, we consider to estimate $1/N_{\rm m}$ by estimating $\pi_{\rm MO}$. By definition of $\pi_{\rm MO}$, we can set its estimator by $H_{\rm MO}^{\rm obs}/(n_{\rm M}n_{\rm O})$, where $H_{\rm MO}^{\rm obs}$ denotes the observed number of MO pairs in a sample. Thus, using Eq.~\ref{pi_MO}, the estimator can be determined as follows:  
\begin{eqnarray}
\widehat{\left(\frac{1}{N_{\rm m}}\right)} &=& \widehat{\pi_{\rm MS}}\nonumber\\
 &=& \frac{H_{\rm MO}^{\rm obs} } {n_{\rm M}n_{\rm O}}.
\label{N_inv_hat}
\end{eqnarray}
Equation~\ref{N_inv_hat} provides a linear estimator of $1/N_{\rm m}$, thus this estimator also works well. Meanwhile, the inverse of the right-hand side in Eq.~\ref{N_inv_hat} is a standard (moment) estimator of $N_{\rm m}$ in the context of CKMR \cite[]{bravington2016close}.
